COG-ED Manuscript

### 2022-01-03 06_Paper/COG-ED/Manuscript.Rmd
changed typo

  # calculate mean reaction time per participant per level

@@

  # ANOVA with three linear contrasts, contrasting the mean rt of two n-back levels (2,3,4) at a time

@@

      hypothesis1c_emm <- emmeans(object = hypothesis1c_performance_rmanova$aov, specs = "level")
      hypothesis1c_peformance_contrasts <- pairs(hypothesis1c_emm)

>>>>

  # calculate median reaction time per participant per level

@@

  # ANOVA with three linear contrasts, contrasting the median rt of two n-back levels (2,3,4) at a time

@@

      hypothesis1c_emm <- emmeans(object = hypothesis1c_performance_rmanova$aov, specs = "level")
      hypothesis1c_performance_contrasts <- pairs(hypothesis1c_emm)
